Reviewer comments from PeerJ

### 2015-03-06 Supplement_mbh.tex
Edits
Edits to supplement regarding gel image.

% Appendix S4. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2GelPeerJ.png}
   \flushleft{Figure S2: Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

>>>>

% Appendix S4. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2GelPeerJ_pretty.png}
   \flushleft{Figure S2: Agarose gel image of amplification products for genotyping of the \emph{Hopscotch} element. Lanes 1 (HopF/HopR; 5kb band) and 2 (HopF/HopIntR; 1.1kb) are the products for one individual that is homozygous for the element; 3 (HopF/HopR; 5kb band) & 4 (HopF/HopIntR; 1.1kb) are also the products of an individual that is homozygous for the element; and 5 (HopF/HopR; 300bp) & 6 (HopF/HopIntR; N/A)  are the products of an individual that is homozygous for the teosinte (lacking the \emph{Hopscotch}) allele.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------
